Get utilization standards and piece size by FMU and township

### 2021-09-29 analysis/get_util_piece_size.Rmd
corrected util.csv and piecesize.csv

tabyl(util_piece_fmu_twp_species,max_species,CD,show_na = TRUE)
head(util_piece_fmu_twp_species)
util_piece_fmu_twp_species
```

>>>>

stuff <- util_piece_fmu_twp_species %>%
  select(max_species,stumpht,stumpd,topd,merch_len,piece_size)

dbhCalcInput <- unique(stuff)

save(dbhCalcInput, file="../data/dbhCalcInput.Rdata")

tabyl(util_piece_fmu_twp_species,max_species,CD,show_na = TRUE)
head(util_piece_fmu_twp_species)
util_piece_fmu_twp_species
dbhCalcInput
```
